Proposed title: The Noisy Work of Uncertainty Visualisation Research

### 2025-12-04 twopagesummary/summary.qmd
maybe i made some more changes and didn't push

Better ways of including a representation of the uncertainty in a data visualisation is a focus of recent research activity. A problem with the current literature is that there is a lack of clarity in the definition of uncertainty, and what it means to represent it in a plot. This confusion can also be seen in literature describing experiments to test effectiveness of choices of different uncertainty representation. The purpose of this review article is to summarise the current literature, provide workable definitions, and illustrate with examples. It is hope that it will be useful to guide new graphics methodology and  experimental work.

>>>>

Better ways of including representation of the uncertainty in a data visualisation is a focus of recent research activity. A problem with the current literature is that there is a lack of clarity about the definition of uncertainty, and what it means to represent it in a plot. This confusion can also be seen in the literature describing experiments on the effectiveness of different uncertainty representation. The purpose of this review article is to summarise the current literature, provide workable definitions, and illustrate these with examples. It is hoped that it will be useful for guiding new graphics methodology and experimental research.
